How many researchers use 'boilerplate' statistical analysis sections?

### 2021-03-09 manuscript/draft_manuscript.Rmd
Update draft_manuscript.Rmd

>>>>

[Figure here or as supplementary - 5 topic solution]

Results of topic modelling assuming five clusters showed clear separation between statistical software, hypothesis testing and linear modelling (Figure). The largest cluster, representing 48% of all included studies (Topic 2, n = 53,491).

Two topics (26% of study sample) were dominated by terms related statistical software, notably Prism/GraphPad (Topic 3, n = 10,940) and SPSS (Topic 5, n = 18,029). Remaining topics focussed on hypothesis testing (Topic, n = 12,531) and analysis of variance/multiple comparisons (Topic 4, n = 16,740)

[Figure here or as supplementary - 10 topic solution]
